---
title: "Critical Value for a Confidence Interval"
author: "Diana Šimić"
date: "September 2021"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

How do we find the critical value for computing a margin of error for a confidence interval based on normal distribution? This animation displays the relationship between the confidence level and the critical value. For a confidence level $C$ , the critical value is the $C+\frac{1-C}{2}$-th quantile of the standard normal distribution. The green area is $C$, and the two red areas together are $1-C$.

```{r echo = F}
inputPanel(
  sliderInput("C", label = "Razina pouzdanosti",
              min = 0.6, max = 0.99, value = 0.9, step = 0.01, width = "300%"))
```

```{r echo = F, fig.height=6, fig.width=4}
renderPlot({
   x <- seq(-4, 4, length.out = 10000)
   y <- dnorm(x)
   C <- input$C
   k2 <- (C+1) / 2
   k1 <- 1 - k2
   op <- par(no.readonly = T)
   par(mar = c(5, 7, 1, 1))
   par()
   plot(x, y, type = "l", lwd = 2, xlab = "", ylab = "Gustoća", 
        axes = F, cex.lab = 2)
   axis(1, pos = 0, cex.axis = 1.5)
   axis(2, las = 1, cex.axis = 1.5)
   z1 <- qnorm(k1)
   z2 <- qnorm(k2)
   abline(v = c(z1, z2), lty = 2, lwd = 2, col = "red")
   x1 <- seq(z1, z2, length.out = 1000)
   y1 <- dnorm(x1)
   polygon(c(x1, rev(x1)),
           c(y1, rep(0, length(x1))),
           col = "green")
   text(0, .2, paste("C = ", C), col = "red", cex = 2.5)
   x2 <- seq(-4, z1, length.out = 1000)
   y2 <- dnorm(x2)
   polygon(c(x2, rev(x2)),
           c(y2, rep(0, length(x2))),
           col = "red")
   x3 <- seq(z2, 4, length.out = 1000)
   y3 <- dnorm(x3)
   polygon(c(x3, rev(x3)),
           c(y3, rep(0, length(x3))),
           col = "red")
   text((z1-4)/2, 0.2, 
        substitute(frac((1-C),2)==k1, list(k1=formatC(k1, format="f", digits=3))), 
        col = "red", cex = 2)
   text((z2+4)/2, 0.2, formatC(k1, format="f", digits=3), col = "red", cex = 2)
   mtext(substitute(paste("z*=",z[k2],"=",z2, sep=""), list(k2=formatC(k2, format="f", digits=3), z2=formatC(z2, format="f", digits = 3))), 
         1, 3, at = z2, cex = 2, col = "red", adj = 0)
   mtext(substitute(paste(z[k1],"=-z*",sep=""), 
                    list(k1 = formatC(k1, format="f", digits=3),
                         k2 = formatC(k2, format="f", digits=3),
                         z1 = formatC(z1, format="f", digits=3))),
         1, 3, at = z1, cex = 2, col = "red", adj = 1)
   par(op)
})
```

